\chapter*{Statement of Contributions}
\addcontentsline{toc}{chapter}{Statement of Contributions}
\setheader{Statement of Contributions}
Some of the work presented in this thesis was completed as part of coauthored works and the main body of this thesis reflects the contributions made as the primary author. Where the work as a secondary author has been presented, it has been significantly abridged to emphasise only the significant contribution of the author of this thesis and the same has been acknowledged in the text. 

In section~\ref{sec:ChemPotExp}, the following two articles have been used with permission from the publisher:
\begin{enumerate}{\small \compresslist
    \item {P.\ Bajpai}, {M.\ Poschmann}, {M.H.A.\ Piro}, \textit{Derivations of useful partial molar excess Gibbs energy of mixing expressions of common thermodynamic models}, {Journal of Phase Equilibria and Diffusion, 42 (2021) 333-347}. 
The author of this thesis was solely responsible for performing the analysis and mathematical derivations and was co-responsible for the verification along with M.\ Poschmann. The author also wrote the majority of the manuscript. 
    
    \item {M.\ Poschmann}, {P.\ Bajpai}, {B.W.N.\ Fitzpatrick}, {M.H.A.\ Piro}, \textit{Recent developments for molten salt systems in Thermochimica}, {Calphad, 75 (2021) 102341}. 
Thesis author's main contribution was the analysis of the MQMQA and derivation of expressions presented in section 2 of the article. Both these activities were performed in conjunction with the primary author of the paper. As such, only section 2 has been presented here and the other sections of the article which do not represent the author's contribution have been omitted.
   }
\end{enumerate}


In section~\ref{sec:algo_choice}, the article: {P.\ Bajpai}, {M.H.A.\ Piro}, \textit{Corrigendum to `The thermochemistry library Thermochimica'}, {Computational Materials Science, 198 (2021) 110659}, has been used with permission from the publisher. The author of this thesis carried out all the analysis and wrote the manuscript. M.H.A. Piro conceptualised and revised the manuscript.

The work described in chapter~\ref{chap:implementation} was performed, in part, during a virtual internship at the Idaho National Laboratory (Idaho Falls, Idaho, United States). The work was performed under the supervision of Dr. D. Schwen and the thesis author was responsible for design and implementation of the software. Dr. D. Schwen reviewed the code and suggested minor code patches.

In section~\ref{sec:interpret_res}, the article {M.H.A.\ Piro}, {M.\ Poschmann}, {P.\ Bajpai}, \textit{On the interpretation of chemical potentials computed from equilibrium thermodynamic codes: Applications to molten salts}, {Journal of Nuclear Materials, 526 (2019) 151756} was used with permission from the publisher. Thesis author contributed to the discussion which evolved into the letter and co-authored the example section of the manuscript.

In section~\ref{sec:gem_pf}, results from a coupled simulation are presented. This work was performed in collaboration with C. Bhave of the University of Florida. The author of this thesis was responsible for the development of the thermodynamic equilibrium solver and for all the thermodynamic calculations performed as part of the simulation. C. Bhave performed the phase-field part of the simulation.